ICM testing

### 2023-10-16 Scripts/Paper_1.Rmd
Tuning completed
Backwards and forwards are working nicely now.  Next up getting other metrics.

source(paste0(loc,"/Scripts/functions/backwards_sim.R"))
source(paste0(loc,"/Scripts/functions/tuning_sim.R"))

@@

# Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
#Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
# Esmarki doesn't work great as it is assessed using a quarterly modle.
#Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]

years.tmp <- NULL
pnm.tmp <- NULL
waa.tmp <- NULL
ages.tmp <- NULL
rem.tmp <- NULL
mx.tmp <- NULL
NE.tmp <- NULL
vpa.tmp <- NULL
am.tmp <- NULL
mr.tmp <- NULL
for(i in Stocks)
{
  print(i)
  ASR_sub <- ASR_long %>%
    dplyr::select(Year, Stock, type, age, value) %>%
    dplyr::filter(Stock==i)

@@

  age.mat <- ASR_sub %>% dplyr::filter(type=="AM") %>% dplyr::rename(AM=value) %>% dplyr::select(-type)
  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
  # in case that changes later...
  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0

  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
  nat.mort <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
  abund <- ASR_sub %>% dplyr::filter(type=="Num") %>% dplyr::rename(Num=value) %>% dplyr::select(-type)
  weight.age <- ASR_sub %>% dplyr::filter(type=="WA") %>% dplyr::rename(WA=value) %>% dplyr::select(-type)
  removals <- ASR_sub %>% dplyr::filter(type=="Catch") %>% dplyr::rename(Catch=value) %>% dplyr::select(-type)

 # if(i=="ICES-WGBFAS_BS 22-32_Sprattus_sprattus") removals$Catch <- removals$Catch/1000

  data <- age.mat %>%
    full_join(nat.mort) %>%
    full_join(abund) %>%
    full_join(weight.age) %>%
    full_join(removals)

  # Aahh??  Is this NA dropping useful data, needed to quick fix the age at maturity data...
  data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
  data <- data[data$available==T,]

@@

  N.end <- sum(data[data$Year==max(years),]$Num)
  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)

  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
  #minage
  minage <- min(as.numeric(data$age))
  #maxage
  maxage <- max(as.numeric(data$age))
  #recruits
  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
  #ssn
  data$ssn <- data$Num * data$AM
  #ssb
  data$ssb <- data$ssn * data$WA #I need to figure out how to line this up with the number of recruits for the right years in the data object.... got it right for the overall r.p.ssb below.
  #tot.ssb
  annual <- data %>% group_by(Year) %>% summarize(tot.ssb = sum(ssb)) %>% left_join(annual)

@@

  #r.p.ssb This needs to be offset by the age of recruits
  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+1):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage)])
  # recs.per.age
  data <- left_join(data, annual)
  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
  tmp <- NULL
  for(j in 1:length(years))
  {
    tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
    tst$Year <- tst$Year + minage
    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
    tmp[[j]] <- tst
  }
  # Unpack the list
  ssb.off <- do.call('rbind',tmp)
  # And merge it with the data object
  data <- left_join(data,ssb.off,by=c("Year","age"))
  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
  # mx
  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
  # This works because 'males' is also in 'females'
  if(grepl("males",i)) data$mx <- data$recs.per.age/data$ssn.offset 
  if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
  # Easier to remove the years where we don't have recs.per.age...
  #data <- data %>% dplyr::filter(Year %in% years[(minage+1):length(years)])
  # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...

@@

  # Dealing with some annoying NAs...
  if(i == "AFSC_BSAI-Males_Pleuronectes_quadrituberculatus")
  {
    age.mat[length(years),] <- age.mat[length(years)-1,]
    prop.nat.mort[length(years),] <- prop.nat.mort[length(years)-1,]
    weight.age[length(years),] <- weight.age[length(years)-1,]
    mx[length(years),13:23] <- mx[length(years),12]
  }

  if(i == "DFO_2J3KL_Gadus_morhua")
  {
    age.mat[,8:10] <- 1
    prop.nat.mort[,8:10] <- prop.nat.mort[,7]
    weight.age[12:14,9:10] <- weight.age[12:14,8]
    weight.age[15,10] <- weight.age[15,9]
    mx[12:16,9:10] <- mx[12:16,8]
    mx[17,10] <- mx[17,9]
  }

  if(i == "DFO_4T-Spring_Clupea_harengus")
  {
    age.mat[6:7,10] <- 1
    prop.nat.mort[6:7,10] <- prop.nat.mort[6:7,9]
    weight.age[6:7,10] <- weight.age[6:7,9]
    mx[6:9,10] <- mx[6:9,9]
  }

  if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
  {
    age.mat[30,8] <- 1
    prop.nat.mort[30,8] <- prop.nat.mort[30,7]
    weight.age[30,8] <- weight.age[29,8]
    mx[30:31,8] <- mx[30:31,9]
  }

  if(i == "ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax")
  {
    age.mat[c(14,27,40),5] <- age.mat[1,5]
    prop.nat.mort[c(14,27,40),5] <- prop.nat.mort[1,5]
    weight.age[c(14,27,40),5] <- weight.age[c(13,26,39),5]
    mx[c(14,16,27,29,40,42),5] <- mx[c(14,16,27,29,40,42),6]
  }

  # For the years of mx without SSB info to inform them
  if(minage >0 ) 
  {
    mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
    names(mx) <- names(mx.fill)
   # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
    mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
  }
  years.tmp[[i]] <- years
  pnm.tmp[[i]] <- prop.nat.mort
  waa.tmp[[i]] <- weight.age
  ages.tmp[[i]] <- minage:maxage
  rem.tmp[[i]] <- rem
  mx.tmp[[i]] <- mx
  NE.tmp[[i]] <- N.end
  vpa.tmp[[i]] <- vpa.abund
  am.tmp[[i]] <- age.mat
  mr.tmp[[i]] <- missing_rem
} #end input data loop

save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,am.tmp,Stocks,ASR_stocks,ASR_long,file =  paste0(loc,"/Results/model_inputs.Rdata"))

```{r, run-mods,echo=F, message=F, warning=F}

load(file = paste0(loc,"/Results/model_inputs.Rdata"))

back.res <- NULL
back.ts <- NULL
back.ts.quants <- NULL
for.res <- NULL
for.ts <- NULL
for.ts.quants <- NULL
tuned.res <- NULL
for(i in Stocks)
{
  years <- years.tmp[[i]]
  prop.nat.mort <- pnm.tmp[[i]] 
  weight.age <- waa.tmp[[i]] 
  ages <- ages.tmp[[i]] 
  rem <- rem.tmp[[i]] 
  mx <- mx.tmp[[i]] 
  N.end <- NE.tmp[[i]] 
  vpa.abund <- vpa.tmp[[i]] 
  age.mat <- am.tmp[[i]]
  # 
  # # The first run gives us the mean estimate, I think that's all we need for our first paper
  tst <- back.sim(years,
                 mat.age = age.mat,
                 nm = -(log(1-prop.nat.mort)),
                 w.age = weight.age,
                 ages = ages,
                 rems = rem$rem,
                 fecund = mx,
                 N.end = N.end,
                 pop.model = 'exponential',
                 n.sims = 1)

  #Combine the data
  did.it.work <- data.frame(abund = c(vpa.abund,tst$Pop$abund),years = c(years,tst$Pop$years),sim = c(rep('VPA',length(years)),tst$Pop$sim))
  # Here get the Upper and lower 50% quantiles to make a functional boxplot
  quants <- did.it.work %>% dplyr::filter(sim != "VPA") %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
                                                                        med = median(abund),
                                                                        U.50 = quantile(abund,probs=c(0.75)))

  back.res[[i]] <- tst
  back.ts[[i]] <- did.it.work
  back.ts.quants[[i]] <- quants

# ################# Now run as a forward simulation
N.start <- vpa.abund[1]

tst <- for.sim(years,
               mat.age = age.mat,
               nm = -(log(1-prop.nat.mort)),
               w.age = weight.age,
               ages = ages,
               rems = rem$rem, # rep(0,nrow(rem)),
               fecund = mx,
               N.start = N.start,
               pop.model = 'exponential',
               n.sims = 1,
               sd.mat = 0,
               sd.nm = 0,
               sd.wt = 0,
               sd.fecund = 0)

  #Combine the data
  did.it.work <- data.frame(abund = c(vpa.abund,tst$Pop$abund),years = c(years,tst$Pop$years),sim = c(rep('VPA',length(years)),tst$Pop$sim))
  # Here get the Upper and lower 50% quantiles to make a functional boxplot
  quants <- did.it.work %>% dplyr::filter(sim != "VPA") %>% dplyr::group_by(years) %>% dplyr::summarise(L.50 = quantile(abund,probs=c(0.25)),
                                                                        med = median(abund),
                                                                        U.50 = quantile(abund,probs=c(0.75)))

  for.res[[i]] <- tst
  for.ts[[i]] <- did.it.work
  for.ts.quants[[i]] <- quants

} # end i in Stocks look

# Save all these
saveRDS(object = back.res,file = paste0(loc,"/Results/backwards_sim_results_no_error.Rds"))
saveRDS(object = back.ts,file = paste0(loc,"/Results/backwards_sim_ts_summaries_no_error.Rds"))
saveRDS(object = back.ts.quants,file = paste0(loc,"/Results/backwards_sim_ts_quantiles_summaries_no_error.Rds"))
# Forward simulations, just using the 'realization'
saveRDS(object = for.res,file = paste0(loc,"/Results/forwards_sim_results_no_error.Rds"))
saveRDS(object = for.ts,file = paste0(loc,"/Results/forwards_sim_ts_summaries_no_error.Rds"))
saveRDS(object = for.ts.quants,file = paste0(loc,"/Results/forwards_sim_ts_quantiles_summaries_no_error.Rds"))

```{r}

# Upack the back.res object...

tst.for <- NULL
tst.back <- NULL
count = 0
for(i in Stocks)
{
  count=count+1
  tmp.for <- for.res[[i]]$r %>% dplyr::filter(n.sims==1)
  tmp.for <- data.frame(tmp.for,stock = i,direction = 'forward simulations',id = count)
  tmp.pop.for <- for.res[[i]]$Pop %>% dplyr::filter(sim==1)
  tst.for[[i]] <- left_join(tmp.pop.for,tmp.for,by=c('years'))
  # backwards
  tmp.back <- back.res[[i]]$r %>% dplyr::filter(n.sims==1)
  tmp.back <- data.frame(tmp.back,stock = i,direction = 'backwards simulations',id = count)
  tmp.pop.back <- back.res[[i]]$Pop %>% dplyr::filter(sim==1)
  tst.back[[i]] <- left_join(tmp.pop.back,tmp.back,by=c('years'))
}

fors <- do.call('rbind',tst.for)
fors <- fors[,-4]
backs <- do.call('rbind',tst.back)

exploring <- rbind(fors,backs)
mn.r <- exploring %>% dplyr::group_by(stock,direction,id) %>% dplyr::summarise(r = median(r,na.rm=T),
                                                                  pop.ratio = dplyr::last(abund)/dplyr::first(abund))
windows(11,11)
ggplot(mn.r) + geom_text(aes(r,pop.ratio,label=id)) + scale_y_log10() + facet_wrap(~direction) + xlab("mean instrinc rate of growth (r)") + ylab("N (Final) / N (Initial)")

quantile(mn.r$r,probs = seq(0.01,1,by=0.01),na.rm=T)

@@

load(file = paste0(loc,"/Results/model_inputs.Rdata"))

back.res <- NULL
back.ts <- NULL
back.ts.quants <- NULL
for.res <- NULL
for.ts <- NULL
for.ts.quants <- NULL
tuned.res <- NULL
for(i in Stocks)
{
  years <- years.tmp[[i]]
  prop.nat.mort <- pnm.tmp[[i]] 
  weight.age <- waa.tmp[[i]] 
  ages <- ages.tmp[[i]] 
  rem <- rem.tmp[[i]] 
  mx <- mx.tmp[[i]] 
  N.end <- NE.tmp[[i]] 
  vpa.abund <- vpa.tmp[[i]] 
  age.mat <- am.tmp[[i]]
  N.end <- vpa.abund[length(vpa.abund)]

   back.tunes <- tune.sim(years,
                          tuner = 'f',
                           n.steps = 250, step.size = 0.2,
                           abund.ts = vpa.abund,
                           mat.age = age.mat,
                           nm = -(log(1-prop.nat.mort)),
                           w.age = weight.age,
                           ages = ages,
                           rems = rem$rem,
                           fecund = mx,
                           N.init = N.end,
                           pop.model = 'exponential',
                           direction='backwards')

   back.tuned.res[[i]] <- back.tunes

   N.start <- vpa.abund[1]

   for.tunes   <- tune.sim(years,
                           tuner='f',
                           n.steps =250, step.size =0.2,
                           abund.ts = vpa.abund,
                           mat.age = age.mat,
                           nm = -(log(1-prop.nat.mort)),
                           w.age = weight.age,
                           ages = ages,
                           rems = rem$rem,
                           fecund = mx,
                           N.init = N.start,
                           pop.model = 'exponential',
                           direction= 'forwards')

   for.tuned.res[[i]] <- for.tunes

@@

>>>>

source(paste0(loc,"/Scripts/functions/tuning_sim_fast.R"))

@@

# Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
#Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
# Esmarki doesn't work great as it is assessed using a quarterly model.
#Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]

years.tmp <- NULL
pnm.tmp <- NULL
waa.tmp <- NULL
ages.tmp <- NULL
rem.tmp <- NULL
mx.tmp <- NULL
NE.tmp <- NULL
vpa.tmp <- NULL
am.tmp <- NULL
mr.tmp <- NULL
all.abund.tmp <- NULL
full.abund.tmp <- NULL
for(i in Stocks)
{
  print(i)
  ASR_sub <- ASR_long %>%
    dplyr::select(Year, Stock, type, age, value) %>%
    dplyr::filter(Stock==i)

  # Drop the NA years....
  if(i == "ICES-NWWG_ICE-Summer_Clupea_harengus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1986)
  # There's some funkiness going on in the first 7 years of these data, so staring in year 8
  if( i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1971)
  if(i == "ICES-NWWG_FA5b_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)
  if(i == "ICES-NWWG_FA5a_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1984)
  if(i == "ICES-AFWG_NEA1-2_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1969)
  if(i == "ICES-WGCSE_CS27.6a_Merlangius_merlangus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1980)
  if(i == "ICES-WGCSE_NS6a_Gadus_morhua") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1980)
  if(i == "ICES-AFWG_COASTNOR 1-2_Gadus_morhua") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 2006)
  if(i == "NEFSC_5Z_Pseudopleuronectes_americanus")ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)

@@

  age.mat <- ASR_sub %>% dplyr::filter(type=="AM") %>% dplyr::rename(AM=value) %>% dplyr::select(-type)
  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
  # in case that changes later...
  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
  am.3s <- length(which((!is.na(age.mat$AM[age.mat$age ==3]))))
  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0
  if(am.3s == 0) age.mat$AM[age.mat$age ==3] <- 0

   # Now we can get the abundance from the VPA models
  abund <- ASR_sub %>% dplyr::filter(type=="Num") %>% dplyr::rename(Num=value) %>% dplyr::select(-type)

  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
  # Now do something similar for the Natural moralities, but in this case
  # we take the NM of the youngest age class we have information for and back that number up to year 0.
  # DK NOTE:  THIS IS A BIG CHANGE IN DIRECTION FOR THE LOTKA CALCS SO NEED TO NOTE THIS ONE!!

  nm.tmp <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
  #minage
  minage <- min(as.numeric(nm.tmp$age[!is.na(nm.tmp$NM)]))
  if(minage == 0)  nat.mort <- nm.tmp
  # Some specials...
  if(i %in% c("ICES-WGCSE_CS7e-k_Gadus_morhua","ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus",
              "ICES-WGHANSA_SP8abd_Sardina _pilchardus","ICES-WGWIDE_NEA 1-9,12,14_Micromesistius_poutassou")) minage <- 1
  if(i == "ICES-WGWIDE_NEA 1,2,5,4a,14a_clupea_ harengus") minage <- 2
  #maxage
  maxage <- max(as.numeric(nm.tmp$age[!is.na(nm.tmp$NM)]))
  # Set up the full abundance matrix 
  full.abund <- abund
  # If we need to imput some data run this loop for natural mortality
  if(minage == 0) full.abund <- abund

  if(minage > 0)
  {
    yrs <- sort(unique((nm.tmp$Year)))
    nm.res <- NULL
    if(!i %in% c("ICES-WGCSE_CS7e-k_Gadus_morhua","ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus",
                 "ICES-WGHANSA_SP8abd_Sardina _pilchardus","ICES-WGWIDE_NEA 1,2,5,4a,14a_clupea_ harengus",
                 "ICES-WGWIDE_NEA 1-9,12,14_Micromesistius_poutassou"))
    {
      for(y in 1:(length(yrs)))
      {
        tmp <- nm.tmp %>% dplyr::filter(Year == yrs[y])
        tmp.abund <- abund %>% dplyr::filter(Year == yrs[y])
        min.nm <- tmp$NM[tmp$age == minage]
        tmp$NM[as.numeric(tmp$age) < minage] <- min.nm
        # Now save these mudders...
        nm.res[[y]] <- tmp
      } # end years loop
      nat.mort <- do.call('rbind',nm.res)
    }
  # Now do the same loopiness for abundance
    for(y in length(yrs):2)
    {
      # The minage of the natural mortality is different from minage of the abundance, annoyingly for this stock...
      if(i == "ICES-AFWG_NEA1-2_Gadus_morhua") minage <- 3
      if(i == "ICES-NWWG_ICE-Summer_Clupea_harengus") minage <- 3

      # for(a in (minage-1):0)
      # {
      #   start.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == a+1) %>% dplyr::pull(Num)
      #   nm.calc <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][a+1,]$NM) 
      #   full.abund[full.abund$Year ==yrs[y]-1,][a+1,]$Num <- start.abund/(1-nm.calc)
      # }

        #if(minage >1 & y == 1)
        #{
           # The lowest minage =4, This goes first since we go backwards, this gets us age 3 in year 3
           if(minage ==4) 
           {
               four.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 4) %>% dplyr::pull(Num)
               nm.four <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][4,]$NM) 
               full.abund[full.abund$Year ==yrs[y]-1,][4,]$Num <- four.abund/(1-nm.four)
             #}# end my 2:0
           } # end if minage ==4

            # The minage =3 scenario, goes after 4...
           if(minage >=3)
           {
             # for(my in 0:1)
             # {
               three.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 3) %>% dplyr::pull(Num)
               nm.three <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][3,]$NM) 
               full.abund[full.abund$Year ==yrs[y]-1,][3,]$Num <- three.abund/(1-nm.three)
             #} # end my 1:0
           } # end if(minage ==2)

           # The minage =2 scenario, this goes last
           if(minage >=2)
           {
             two.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 2) %>% dplyr::pull(Num)
             nm.two <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][2,]$NM) 
             full.abund[full.abund$Year ==yrs[y]-1,][2,]$Num <- two.abund/(1-nm.two)
           } # end if(minage ==2)

           if(minage >=1)
           {
             one.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 1) %>% dplyr::pull(Num)
             nm.one <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][1,]$NM) 
             full.abund[full.abund$Year ==yrs[y]-1,][1,]$Num <- one.abund/(1-nm.one)
           } # end if(minage ==2)

         } # The annoying if to fill in rest of the first few years.
  } # end if minage > 0

  # We won't have a weight at age for the young ages, which is fine since we only need that for SSB
  weight.age <- ASR_sub %>% dplyr::filter(type=="WA") %>% dplyr::rename(WA=value) %>% dplyr::select(-type)
  removals <- ASR_sub %>% dplyr::filter(type=="Catch") %>% dplyr::rename(Catch=value) %>% dplyr::select(-type)
  # Fill the leading NAs with 0s now...
  if(minage > 0) 
  {
    weight.age$WA[weight.age$age %in% 0:(minage-1)] <- 0
    removals$Catch[removals$age %in% 0:(minage-1)] <- 0
  }
 # if(i=="ICES-WGBFAS_BS 22-32_Sprattus_sprattus") removals$Catch <- removals$Catch/1000

  data <- age.mat %>%
    full_join(nat.mort) %>%
    #full_join(abund) %>%
    full_join(full.abund) %>%
    full_join(weight.age) %>%
    full_join(removals)

  # Nice way to toss NAs!
  data$available <- apply(is.na(data[, c("AM", "Num", "WA")]), 1, function(x) all(!x==T))
  data <- data[data$available==T,]
  # And then toss the years we don't have 0 data for Numbers in the 0 age class
  toss.years <- data %>% dplyr::group_by(Year) %>% dplyr::reframe(bad.years = which(min(age)>0))
  data <- data[!data$Year %in% toss.years$Year,]

@@

  N.end <- sum(data[data$Year==max(years),]$Num)
  all.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::filter(age >= minage) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..

  #recruits
  annual <- data.frame(Year=data$Year[data$age==0], recruits=data$Num[data$age==0])
  #ssn
  data$ssn <- data$Num * data$AM
  #ssb
  data$ssb <- data$ssn * data$WA #I need to figure out how to line this up with the number of recruits for the right years in the data object.... got it right for the overall r.p.ssb below.
  #tot.ssb
  annual <- data %>% group_by(Year) %>% summarize(tot.ssb = sum(ssb)) %>% left_join(annual)

@@

  #r.p.ssb This no longer needs any offset...
  annual$r.p.ssb <- annual$recruits/annual$tot.ssb
  # recs.per.age
  data <- left_join(data, annual)
  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
  # tmp <- NULL
  # for(j in 1:length(years))
  # {
  #   tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
  #   tst$Year <- tst$Year + minage
  #   names(tst) <- c("ssb.offset","ssn.offset","Year","age")
  #   tmp[[j]] <- tst
  # }
  # Unpack the list
  #@ssb.off <- do.call('rbind',tmp)
  # And merge it with the data object
  #data <- left_join(data,ssb.off,by=c("Year","age"))
  data$recs.per.age <- data$ssb*data$r.p.ssb
  # mx
  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
  # This works because 'males' is also in 'females'
  if(grepl("males",i)) data$mx <- data$recs.per.age/data$ssn 
  if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn/2 # Moms only! 
  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
  # Easier to remove the years where we don't have recs.per.age...
  #data <- data %>% dplyr::filter(Year %in% years[(minage+1):length(years)])
  # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...

@@

  # Dealing with some annoying NAs...
  # if(i == "AFSC_BSAI-Males_Pleuronectes_quadrituberculatus")
  # {
  #   age.mat[length(years),] <- age.mat[length(years)-1,]
  #   prop.nat.mort[length(years),] <- prop.nat.mort[length(years)-1,]
  #   weight.age[length(years),] <- weight.age[length(years)-1,]
  #   mx[length(years),13:23] <- mx[length(years),12]
  # }
  # 
  if(i == "DFO_2J3KL_Gadus_morhua")
  {
    age.mat[,10:12] <- 1
    prop.nat.mort[,10:12] <- prop.nat.mort[,9]
    weight.age[12:14,11:12] <- weight.age[12:14,10]
    weight.age[15,12] <- weight.age[15,11]
    mx[12:14,11:12] <- mx[12:14,10]
    mx[15,12] <- mx[15,11]
  }

  if(i == "DFO_4T-Spring_Clupea_harengus")
  {
    age.mat[6:7,12] <- 1
    prop.nat.mort[6:7,12] <- prop.nat.mort[6:7,11]
    weight.age[6:7,12] <- weight.age[6:7,11]
    mx[6:7,12] <- mx[6:7,11]
  }

  if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
  {
    age.mat[30,9] <- 1
    prop.nat.mort[30,9] <- prop.nat.mort[30,8]
    weight.age[30,9] <- weight.age[29,9]
    mx[30,9] <- mx[30,8]
  }

  if(i == "ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax")
  {
    age.mat[c(14,27,40),7] <- age.mat[1,7]
    prop.nat.mort[c(14,27,40),7] <- prop.nat.mort[1,7]
    weight.age[c(14,27,40),7] <- weight.age[c(13,26,39),7]
    mx[c(14,27,40),7] <- mx[c(14,27,40),6]
  }
  # Clear out some 0's...
  if( i == "AFSC_EEBSAI_Limanda_aspera")
  {
    mx[4,19] <- mean(unlist(mx[4,c(18,20)]))
    mx[c(5,7),20] <- mx[c(5,7),19]
    mx[1:6,21] <- mx[1:6,20] 
  }
  # For the years of mx without SSB info to inform them
  # if(minage >0 ) 
  # {
  #   mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
  #   names(mx) <- names(mx.fill)
  #  # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
  #   mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
  # }
  years.tmp[[i]] <- years
  pnm.tmp[[i]] <- prop.nat.mort
  waa.tmp[[i]] <- weight.age
  ages.tmp[[i]] <- minage:maxage
  rem.tmp[[i]] <- rem
  mx.tmp[[i]] <- mx
  NE.tmp[[i]] <- N.end
  vpa.tmp[[i]] <- vpa.abund
  all.abund.tmp[[i]] <- all.abund
  full.abund.tmp[[i]] <- full.abund
  am.tmp[[i]] <- age.mat
  mr.tmp[[i]] <- missing_rem
} #end input data loop

save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,am.tmp,Stocks,ASR_stocks,ASR_long,all.abund.tmp,full.abund.tmp,file =  paste0(loc,"/Results/model_inputs_all_ages.Rdata"))

@@

load(file = paste0(loc,"/Results/model_inputs_all_ages.Rdata"))

back.tune.all.res <- NULL
back.tune.summary <- NULL
for.tune.all.res <- NULL
for.tune.summary <- NULL
for(i in Stocks)
{
  years <- years.tmp[[i]]
  prop.nat.mort <- pnm.tmp[[i]] 
  rem <- rem.tmp[[i]] 
  mx <- mx.tmp[[i]] 
  N.end <- NE.tmp[[i]] 
  ages <- ages.tmp[[i]]
  vpa.abund <- vpa.tmp[[i]] 
  all.abund <- all.abund.tmp[[i]]
  #N.end <- vpa.abund[length(vpa.abund)]

   N.start <- all.abund[1]
   print(i)
   # The fecundities are 
   fast.for.tune <- fast.tunes(years,
                           tuner='f',
                           step.size = 0.025, # Make sure n.steps is even please!!
                           abund.ts = all.abund,
                           ages=ages,
                           nm = -(log(1-prop.nat.mort)),
                           rems = rem$rem,
                           fecund = mx,
                           N.init = N.start,
                           direction= 'forwards'
                           )

   for.tune.all.res[[i]] <- fast.for.tune
   for.tune.tmp <- data.frame(fast.for.tune$res,Stock = i)
   for.tune.summary[[i]] <- for.tune.tmp

   N.end <- all.abund[length(all.abund)]

   fast.back.tune <- fast.tunes(years,
                           tuner='f',
                           step.size = 0.025, # Make sure n.steps is even please!!
                           abund.ts = all.abund,
                           ages = ages,
                           nm = -(log(1-prop.nat.mort)),
                           rems = rem$rem,
                           fecund = mx,
                           N.init = N.end,
                           direction= 'backwards'
                           )

   back.tune.all.res[[i]] <- fast.back.tune
   back.tune.tmp <- data.frame(fast.back.tune$res,Stock = i)
   back.tune.summary[[i]] <- back.tune.tmp

@@

tst <- do.call('rbind',for.tune.summary)
quantile(tst$per.diff,probs=seq(0.001,1,0.001),na.rm=T)
# summary(tst$per.diff)
# summary(tst$r)
# tst <- tst[abs(tst$per.diff) > 5,]
# 
# range(tst$per.diff,na.rm=T)
# It completed 33 stocks, was on stock 34
saveRDS(back.tune.summary,"D:/Github/ICM/Results/backwards_fully_tuned_summary.Rds")
saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary.Rds")
saveRDS(back.tune.all.res,"D:/Github/ICM/Results/backwards_fully_tuned_all_res.Rds")
saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res.Rds")
